\section{BPX Type: Texture ('T')}

\subsection{Overview}
The Texture BPX is using 'T' as the type byte of BPX Main Header. This type provides optimized and efficient texture storage for 3D rendering APIs.
\newline
Below is a table describing the different sections to be expected in a BPXT:
\begin{center}
    {
        \rowcolors{2}
        {red!15}
        {blue!15}
        \begin{tabular}{|c|c|c|c|}
            \hline
            \textbf{Name} & \textbf{Type} & \textbf{Required} & \textbf{Single Time} \\

            \hline\hline
            PixelArray & 0 & Yes & Yes \\
            \hline
        \end{tabular}
    }
\end{center}

\subsection{TypeExt}
Contains information about the texture encoding.
\begin{center}
    {
        \rowcolors{2}
        {red!15}
        {blue!15}
        \begin{tabular}{|c|c|c|c|}
            \hline
            \textbf{Name} & \textbf{Type} & \textbf{Size} & \textbf{Notes} \\
    
            \hline\hline
            Width & Unsigned & 4 & Texture width \\
            Height & Unsigned & 4 & Texture height \\
            Format & Unsigned & 4 & Texture format \\
            Flags & Unsigned & 4 & Flags \\
            MipMap Level & Unsigned & 8 & Number of mip maps \\
            Array & Unsigned & 16 & Size of texture array (0 = no texture array) \\
            \hline
        \end{tabular}
    }
\end{center}

\subsubsection{Width}
The expected width of all pixel arrays in power of two form ($2^{k+1}$px where k is the stored number).

\subsubsection{Height}
The expected height of all pixel arrays in power of two form ($2^{k+1}$px where k is the stored number).

\subsection{Analysis on texture size storage}
Certain redering APIs requires that the textures are aligned to a specific implementation defined number of pixels per row. This number also called stride is usualy 8 or a power of two greater than 8.\newline
By assuming any BPX encoded texture is encoded with power of twos instead of their actual resolution in pixels, we can eliminate the need, in the cases where the implementation uses power of two strides, to run a padding alignment before presenting the texture to this implementation. Also this allows to reduce the field size for storing texture size: instead of using 32 bits or 64 bits we can store a texture size in 8 bits and keep relatively large texture sizes, \textbf{optimizing both storage space and application load speed}. Indeed the maximum texture size in each direction allowed by BPX would be $2^{15 + 1} = 2^{16} = 65536$. Most rendering API implementation do not support such large texture sizes.\newline
From there one might say that we should then use less than 8 bits. However using less than 8 bits for storing the entire size vector would conflict with hardware indexing as most hardware only indexes 8 bits bytes.

\subsubsection{Format}
Available formats:
\begin{center}
    {
        \rowcolors{2}
        {red!15}
        {blue!15}
        \begin{tabular}{|c|c|c|c|}
            \hline
            \textbf{Name} & \textbf{Value} & \textbf{Notes} \\

            \hline\hline
            RGB & 0x1 & Standard 8 bits 3 channel RGB format \\
            RGBA & 0x2 & 8 bits 4 channel RGB with transparency level \\
            GREY\_SCALE & 0x3 & Single 8 bits channel representing grey scale level \\
            FLOAT & 0x4 & Single channel 32 bits float texture \\
            \hline
        \end{tabular}
    }
\end{center}

\subsubsection{Flags}
Bit mask based flags (or flags together). Currently the only supported flags are:
\begin{center}
    {
        \rowcolors{2}
        {red!15}
        {blue!15}
        \begin{tabular}{|c|c|c|}
            \hline
            \textbf{Name} & \textbf{Value} & \textbf{Notes} \\
    
            \hline\hline
            Array & 0x1 & Indicates the texture should be interpreted as a texture array \\
            Compressed & 0x2 & Indicates the texture should be GPU compressed on load \\
            CubeMap & 0x4 & Indicates the texture should be interpreted as a CubeMap \\
            \hline
        \end{tabular}
    }
\end{center}

\subsubsection{MipMap Level}
Number of mip maps \cite{MipMap} to auto generate when loading this texture.

\subsubsection{Array}
Number of textures for creating a texture array. If this value is 0 consider this is not a texture array.\newline
Ignore this value if neither of Array or CubeMap flags are set.

\subsection{PixelArray}
Texture data array encoded as described by texture format.\newline
If the \textit{Array} value in the header is greater than 0 then a series of \textit{Array} count texture data arrays are saved one after the other encoded with respect to the texture format described by the header.\newline
In case the CubeMap flag is set the \textit{Array} field in the header should be 6 and this section should contain 6 texture data arrays.