\section{Comparison against mainstream formats}
Below is a non-exhaustive table showing the differences between the idea of BPX and existing mainstream formats:
\bpxtable{C|c|c|c|c|c}{Name & Open & DRM & Flexible & Optimized & Compat.}
{
    FBX & \cellcolor{red}No & \cellcolor{green}No & \cellcolor{red}No & \cellcolor{green}Yes & \cellcolor{yellow}Partial \\
    Unreal & \cellcolor{red}No & \cellcolor{red}Yes & \cellcolor{green}Yes & \cellcolor{green}Yes & \cellcolor{yellow}Partial \\
    Unity & \cellcolor{red}No & \cellcolor{red}Yes & \cellcolor{yellow}Partial & \cellcolor{green}Yes & \cellcolor{yellow}Partial \\
    OBJ & \cellcolor{green}Yes & \cellcolor{green}No & \cellcolor{red}No & \cellcolor{red}No & \cellcolor{green}Yes \\
}
\begin{itemize}
    \item FBX: It is possible to save files as Text based FBX however no open documentation exists for the format. The binary FBX requires the use of a closed source library. FBX supports Windows without issues, however getting the SDK to work on different platforms might be an issue.\newline
    FBX is designed to support 3D models.
    \item The source code of Unreal can be accessed if you agree to certain licenses which prohibit the redistribution of the editor source code in the game, preventing the use of Unreal's format as a base to support modding. Also Unreal does not provide easy installation under Linux.\newline
    Unreal is also using a unified format for all assets of the game. It has support for modding however the modder is required to agree to licenses and to download the full SDK.
    \item Unity, although it has better support for Linux, might still be a bit tricky in certain combinations of distribution/system.\newline
    Unity is also using a unified format for all assets of the game but the game engine does not allow load of arbitrary custom assets. The asset format used by unity is also closed and does not permit modification by the player of the game like Unreal.
    \item OBJ is a text based 3D model format. The format has no support for skeletal based models/animations and has poor support for materials.
\end{itemize}